---
title: "ET_ltMemory_glmm"
author: "Christoph Völter"
date: "29 September 2019"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (car)
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(ggplot2)
library(scales)
library(gridExtra)
library(psych)
library(cowplot)
library(glmmTMB)
library(summarytools)
source("../../R scripts/Roger/diagnostic_fcns.r")
source("../../R scripts/Roger/glmm_stability.r")
source("../../R scripts/Roger/boxplotteR.r")
source("../../R scripts/Roger/boot_glmm.r")
source("../../R scripts/Roger/corr_exact.r")
#load(file =".RData")
```

```{r loading data, include = FALSE, warning = FALSE}
#Preparing code for mixed modeling. 
orig.data <- read.table(file="data/ET_lt_memory_AOIreport.txt", header=T, sep="\t")
str(orig.data)
#describeBy(orig.data)

all.data<-orig.data%>%
 # filter(IA_DWELL_TIME__prop!=".")%>%
  #filter(IA_AVERAGE_FIX_PUPIL_SIZE!=".")%>%
  filter(Subject!="lara")%>% #completed only session 2
  droplevels()%>%
  mutate(target = ifelse(location=="left" & IA_LABEL=="AOI_object_left","target",
                         (ifelse(location=="right" & IA_LABEL=="AOI_object_left","distractor",
                                 (ifelse(location=="right" & IA_LABEL=="AOI_object_right","target",
                                         (ifelse(location=="left" & IA_LABEL=="AOI_object_right","distractor",
                                                 (ifelse(location=="left" & IA_LABEL=="Left_half_display","target",
                                                         (ifelse(location=="right" & IA_LABEL=="Left_half_display","distractor",
                                                                 (ifelse(location=="right" & IA_LABEL=="Right_half_display","target",
                                                                         (ifelse(location=="left" & IA_LABEL=="Right_half_display","distractor",""
                                                                                 ))))))))))))))))
table(all.data$target,all.data$IA_LABEL)
#all.data$IA_DWELL_TIME__prop=as.numeric(as.character(all.data$IA_DWELL_TIME__prop))
#all.data$IA_AVERAGE_FIX_PUPIL_SIZE=as.numeric(as.character(all.data$IA_AVERAGE_FIX_PUPIL_SIZE))



view(dfSummary(all.data))

```





##Summary
Both the paired-samples t-test and a mixed model show a significant effect for condition. There was no significant interaction between session and condition. 


##Plotting data

###IP1


```{r error=FALSE, echo=FALSE}

  

plot_target_IP1_obj <- all.data %>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="AOI_object_right" | IA_LABEL=="AOI_object_left")%>%
  filter(target=="target")%>%
  group_by(Session,IA_LABEL, location,Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)

loc.labs <- c("Target on the left", "Target on the right")
names(loc.labs) <- c("AOI_object_left", "AOI_object_right")

p_target_IP1_obj<-ggplot(
  data=plot_target_IP1_obj, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, IA_LABEL)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP1_obj$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target box")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10),axis.title.y = element_text(size=8), plot.title = element_text(size=10), plot.caption = element_text(size=10))+
    facet_wrap(~ IA_LABEL,labeller=labeller(IA_LABEL=loc.labs))
 
p_target_IP1_obj

ggsave(filename = "ET_lt_IP1_IAObj_by_target_side.png", width = 10, height = 8, units = "cm")
```
```{r error=FALSE, echo=FALSE}

  

plot_target_IP1_displ <- all.data %>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  filter(target=="target")%>%
  group_by(Session,IA_LABEL, location,Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)

loc.labs <- c("Target on the left", "Target on the right")
names(loc.labs) <- c("Left_half_display", "Right_half_display")

p_target_IP1_displ<-ggplot(
  data=plot_target_IP1_displ, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, IA_LABEL)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP1_displ$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target side")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10),axis.title.y = element_text(size=8), plot.title = element_text(size=10), plot.caption = element_text(size=10))+
    facet_wrap(~ IA_LABEL,labeller=labeller(IA_LABEL=loc.labs))
 
p_target_IP1_displ

#ggsave(filename = "ET_lt_IP1_IAhalfDisplay_by_target_side.png", width = 10, height = 8, units = "cm")
```

```{r error=FALSE, echo=FALSE}

  

plot_target_IP1_targ <- all.data %>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  group_by(Session,target,Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)


p_target_IP1_targ<-ggplot(
  data=plot_target_IP1_targ, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, target)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP1_targ$n, colour = "darkgrey", alpha=0.25) +
  #geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target side")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
    facet_wrap(~ target)#,labeller=labeller(IA_LABEL=loc.labs))
 
p_target_IP1_targ

#ggsave(filename = "ET_lt_IP1_IAhalfDisplay_by_target_side.png", width = 10, height = 8, units = "cm")
```


```{r error=FALSE, echo=FALSE}

  

plot_target_IP1reach_displ <- all.data %>%
  filter(IP_LABEL=="IP1_reach")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  filter(target=="target")%>%
  group_by(Session,IA_LABEL, Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)

loc.labs <- c("Target on the left", "Target on the right")
names(loc.labs) <- c("Left_half_display", "Right_half_display")

p_target_IP1reach_displ<-ggplot(
  data=plot_target_IP1reach_displ, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, IA_LABEL)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP1reach_displ$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target side")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10),axis.title.y = element_text(size=8), plot.title = element_text(size=10), plot.caption = element_text(size=10))+
    facet_wrap(~ IA_LABEL,labeller=labeller(IA_LABEL=loc.labs))
 
p_target_IP1reach_displ

ggsave(filename = "ET_lt_IP1Reach_IAhalfDisplay_by_target_side.png", width = 10, height = 8, units = "cm")
```
```{r error=FALSE, echo=FALSE}

  

plot_target_IP_AN1_displ <- all.data %>%
  filter(IP_LABEL=="IP_AN1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  filter(target=="target")%>%
  group_by(Session,IA_LABEL, Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)

loc.labs <- c("Target on the left", "Target on the right")
names(loc.labs) <- c("Left_half_display", "Right_half_display")

p_target_IP1_AN1_displ<-ggplot(
  data=plot_target_IP_AN1_displ, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, IA_LABEL)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP_AN1_displ$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target side")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10),axis.title.y = element_text(size=8), plot.title = element_text(size=10), plot.caption = element_text(size=10))+
    facet_wrap(~ IA_LABEL,labeller=labeller(IA_LABEL=loc.labs))

p_target_IP1_AN1_displ

#ggsave(filename = "ET_lt_IP1Reach_IAhalfDisplay_by_target_side.png", width = 10, height = 8, units = "cm")
```
##AOI: Object
```{r error=FALSE, echo=FALSE}

  

plot_target_IP1_obj <- all.data %>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="AOI_object_right" | IA_LABEL=="AOI_object_left")%>%
  filter(target=="target")%>%
  group_by(Session,IA_LABEL, Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)

loc.labs <- c("Target on the left", "Target on the right")
names(loc.labs) <- c("AOI_object_left", "AOI_object_right")

p_target_IP1_obj<-ggplot(
  data=plot_target_IP1_obj, aes(as.factor(Session), prop_dwell, group=Subject)) +   
  geom_boxplot(aes(group=interaction(Session, IA_LABEL)), width=0.9, outlier.colour="white")+
  geom_point(size = plot_target_IP1_obj$n, colour = "darkgrey", alpha=0.25) +
  #geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to target side")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=12), plot.caption = element_text(size=10))+
    facet_wrap(~ IA_LABEL,labeller=labeller(IA_LABEL=loc.labs))
 
p_target_IP1_obj

ggsave(filename = "ET_lt_IP1_IA_AOIObject_by_target_side.png", width = 10, height = 8, units = "cm")
```
##Agent head
```{r error=FALSE, echo=FALSE}

  

plot_head <- all.data %>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="AOI_agent_head")%>%
  group_by(Session,Subject ) %>% 
  summarize(prop_dwell = mean(IA_DWELL_TIME__prop))  %>% 
  mutate(prop_dwell = round(prop_dwell/0.01)*0.01)%>%
  add_count(prop_dwell)



p_head<-ggplot(
  data=plot_head, aes(as.factor(Session), prop_dwell)) +   
  geom_boxplot(aes(as.factor(Session)),width=0.9, outlier.colour="white")+
  geom_point(size = plot_head$n, colour = "darkgrey", alpha=0.25) +
  geom_line(lty=2, alpha=0.4, colour="darkgrey")+
  ylim(0,1)+
  labs(x="Session",y="Proportion looking time to agent head")+
  theme_few()+
  theme(axis.ticks.x=element_blank(), axis.title.x = element_text(size=10), plot.title = element_text(size=10), plot.caption = element_text(size=10))

 
p_head

#ggsave(filename = "ET_lt_IP1_IA_AOIAgentHead_by_session.png", width = 10, height = 8, units = "cm")
```

```{r} 


p<-plot_grid(p_target_IP1_displ, p_target_IP1reach_displ,p_target_IP1_AN1_displ, labels = c('Anticipation phase (3000 ms)', 'Follow hand movement (818 ms)', 'Animal uncovered (4584 ms)'), label_size = 10, label_x = c(-0.25, -0.3, -0.25) , nrow=3)

p2<-plot_grid(p,  ncol=2, rel_widths = c(1,1))

ggdraw(p2) + 
  draw_image("heatmaps/IP_AN1_S1S2.png", x = 1, y = 0.445, hjust = 1, vjust = 1, width = 0.5, height = 0.5)+
    draw_image("heatmaps/IP1_S1S2.png", x = 1, y = 1.11, hjust = 1, vjust = 1, width = 0.5, height = 0.5)+
    draw_image("heatmaps/IP1_reach_S1S2.png", x = 1, y = 0.775, hjust = 1, vjust = 1, width = 0.5, height = 0.5)

ggsave("overview.png", width = 17, height = 22, units = "cm")

```




\pagebreak  
``

``` {r mixed modeling, error=TRUE}

model.data1 <- all.data %>% 
  filter(IP_LABEL=="IP_AN1")%>%
  filter(IA_LABEL=="AOI_object_left" | IA_LABEL=="AOI_object_right")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  spread(target,IA_DWELL_TIME__prop)%>%
  rename(dwell.prop.target=target)%>%
  rename(dwell.prop.distractor=distractor)

model.data <- all.data %>% 
  filter(IP_LABEL=="IP_AN1")%>%
  filter(IA_LABEL=="AOI_object_left" | IA_LABEL=="AOI_object_right")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME)%>%
  spread(target,IA_DWELL_TIME)%>%
  rename(dwell.target=target)%>%
  rename(dwell.distractor=distractor)%>%
  full_join(model.data1)%>%
  mutate(dwell_prop_target_halves=(dwell.target/(dwell.target+dwell.distractor)))%>%
  mutate(dwell_both_halves=(dwell.target+dwell.distractor))%>%
  mutate(Session = as.factor(Session))#%>%
  #drop_na(dwell_prop_target_halves)

ggplot(
  data=model.data, aes(interaction(Session,location), dwell.prop.target)) +   
  geom_boxplot(aes(interaction(Session,location)),width=0.9, outlier.colour="black")

```


individuals only who looked at the animals in session 1
``` {r mixed modeling, error=TRUE}

model.data1 <- all.data %>% 
  filter(Subject=="Aeden"| Subject=="Akina" |Subject=="Calisle" |Subject=="Akina" |Subject=="Chasie" |Subject=="Emily" |Subject=="Gatsby" |Subject=="Kayl" |Subject=="Linus" |Subject=="Maeva" |Subject=="Miley")%>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  spread(target,IA_DWELL_TIME__prop)%>%
  rename(dwell.prop.target=target)%>%
  rename(dwell.prop.distractor=distractor)

model.data <- all.data %>% 
  filter(Subject=="Aeden"| Subject=="Akina" |Subject=="Calisle" |Subject=="Akina" |Subject=="Chasie" |Subject=="Emily" |Subject=="Gatsby" |Subject=="Kayl" |Subject=="Linus" |Subject=="Maeva" |Subject=="Miley")%>%
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME)%>%
  spread(target,IA_DWELL_TIME)%>%
  rename(dwell.target=target)%>%
  rename(dwell.distractor=distractor)%>%
  full_join(model.data1)%>%
  mutate(dwell_prop_target_halves=(dwell.target/(dwell.target+dwell.distractor)))%>%
  mutate(dwell_both_halves=(dwell.target+dwell.distractor))%>%
  mutate(Session = as.factor(Session))%>%
  drop_na(dwell_prop_target_halves)

ggplot(
  data=model.data, aes(interaction(Session,location), dwell_prop_target_halves)) +   
  geom_boxplot(aes(interaction(Session,location)),width=0.9)#, outlier.colour="white")

```



##GLMM for IP1
```{r}


model.data1 <- all.data %>% 
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  spread(target,IA_DWELL_TIME__prop)%>%
  rename(dwell.prop.target=target)%>%
  rename(dwell.prop.distractor=distractor)

model.data <- all.data %>% 
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME)%>%
  spread(target,IA_DWELL_TIME)%>%
  rename(dwell.target=target)%>%
  rename(dwell.distractor=distractor)%>%
  full_join(model.data1)%>%
  mutate(dwell_prop_target_halves=(dwell.target/(dwell.target+dwell.distractor)))%>%
  mutate(dwell_both_halves=(dwell.target+dwell.distractor))%>%
  mutate(Session = scale(Session))

model.data$resp=model.data$dwell.prop.target
model.data$resp <- (model.data$resp*(length(model.data$resp) - 1) + 0.5)/length(model.data$resp) 
model.data<-model.data%>%drop_na(resp)


## code to run the model
mm.ip1.displ=glmmTMB(resp~Session+location+
      (1|Subject)+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))
mm.ip1.displ$sdr$pdHess
summary(mm.ip1.displ)
overdisp.test(mm.ip1.displ)


```
####Null model	 
```{r}	 
mm.ip1.displ.null=glmmTMB(resp~1+
      (1|Subject)+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))

```
####Full-null model comparison
```{r}	 
anova(mm.ip1.displ, mm.ip1.displ.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.ip1.displ)$coefficients$cond, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.ip1.displ, test="Chisq")
round(xdrop1,3)
```






```{r include=FALSE}
## save model output

save.image("mm1_SpaghettiTube_partnerPayoffs.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```



##GLMM for IP1_reach
```{r}


model.data1 <- all.data %>% 
  filter(IP_LABEL=="IP1_reach")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  spread(target,IA_DWELL_TIME__prop)%>%
  rename(dwell.prop.target=target)%>%
  rename(dwell.prop.distractor=distractor)

model.data <- all.data %>% 
  filter(IP_LABEL=="IP1_reach")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME)%>%
  spread(target,IA_DWELL_TIME)%>%
  rename(dwell.target=target)%>%
  rename(dwell.distractor=distractor)%>%
  full_join(model.data1)%>%
  mutate(dwell_prop_target_halves=(dwell.target/(dwell.target+dwell.distractor)))%>%
  mutate(dwell_both_halves=(dwell.target+dwell.distractor))%>%
  mutate(Session = scale(Session))

model.data$resp=model.data$dwell.prop.target
model.data$resp <- (model.data$resp*(length(model.data$resp) - 1) + 0.5)/length(model.data$resp) 
model.data<-model.data%>%drop_na(resp)


## code to run the model
mm.ip1_reach.displ=glmmTMB(resp~Session+location+
      (1|Subject),#+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))
summary(mm.ip1_reach.displ)
overdisp.test(mm.ip1_reach.displ)


```
####Null model	 
```{r}	 
mm.ip1_reach.displ.null=glmmTMB(resp~1+
      (1|Subject),#+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))

```
####Full-null model comparison
```{r}	 
anova(mm.ip1_reach.displ, mm.ip1_reach.displ.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.ip1_reach.displ)$coefficients$cond, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.ip1_reach.displ, test="Chisq")
round(xdrop1,3)
```



```{r include=FALSE}
## save model output

save.image("ET_lt_image.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```


##GLMM for IP_N1
```{r}


model.data1 <- all.data %>% 
  filter(IP_LABEL=="IP_AN1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  spread(target,IA_DWELL_TIME__prop)%>%
  rename(dwell.prop.target=target)%>%
  rename(dwell.prop.distractor=distractor)

model.data <- all.data %>% 
  filter(IP_LABEL=="IP_AN1")%>%
  filter(IA_LABEL=="Left_half_display" | IA_LABEL=="Right_half_display")%>%
  select(Subject,location,target,Session,IP_LABEL, IA_DWELL_TIME)%>%
  spread(target,IA_DWELL_TIME)%>%
  rename(dwell.target=target)%>%
  rename(dwell.distractor=distractor)%>%
  full_join(model.data1)%>%
  mutate(dwell_prop_target_halves=(dwell.target/(dwell.target+dwell.distractor)))%>%
  mutate(dwell_both_halves=(dwell.target+dwell.distractor))%>%
  mutate(Session = scale(Session))

model.data$resp=model.data$dwell.prop.target
model.data$resp <- (model.data$resp*(length(model.data$resp) - 1) + 0.5)/length(model.data$resp) 
model.data<-model.data%>%drop_na(resp)


## code to run the model
mm.ip_an1.displ=glmmTMB(resp~Session+location+
      (1|Subject),#+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))
summary(mm.ip_an1.displ)
overdisp.test(mm.ip_an1.displ)


```
####Null model	 
```{r}	 
mm.ip_an1.displ.null=glmmTMB(resp~1+
      (1|Subject),#+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))

```
####Full-null model comparison
```{r}	 
anova(mm.ip_an1.displ, mm.ip_an1.displ.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.ip_an1.displ)$coefficients$cond, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.ip_an1.displ, test="Chisq")
round(xdrop1,3)
```



```{r include=FALSE}
## save model output

save.image("ET_lt_image.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```






##GLMM for IP1 and the agent face AOI
```{r}


model.data <- all.data %>% 
  filter(IP_LABEL=="IP1")%>%
  filter(IA_LABEL=="AOI_agent_head")%>%
  select(Subject,location,Session,IP_LABEL, IA_DWELL_TIME__prop)%>%
  mutate(Session = scale(Session))

model.data$resp=model.data$IA_DWELL_TIME__prop
model.data$resp <- (model.data$resp*(length(model.data$resp) - 1) + 0.5)/length(model.data$resp) 
model.data<-model.data%>%drop_na(resp)


## code to run the model
mm.ip1_AOIHead=glmmTMB(resp~Session+location+
      (1|Subject)+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))
summary(mm.ip1_AOIHead)
overdisp.test(mm.ip1_AOIHead)


```
####Null model	 
```{r}	 
mm.ip1_reach.displ.null=glmmTMB(resp~1+
      (1|Subject),#+(0+Session|Subject),# weights=dwell_both_halves,#
      data=model.data, family=beta_family, 
      control=glmmTMBControl(optCtrl=list(iter.max=1000000, eval.max=1000000)))

```
####Full-null model comparison
```{r}	 
anova(mm.ip1_reach.displ, mm.ip1_reach.displ.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.ip1_reach.displ)$coefficients$cond, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.ip1_reach.displ, test="Chisq")
round(xdrop1,3)
```



```{r include=FALSE}
## save model output

save.image("ET_lt_image.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```